---
title: "Accessing EU Pre-Legislative Documents via EurLex R Package (Rework)"
author: "Katelyn Nutley"
date: "28-07-2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Introduction

This is a reworking of our first Eurlex scrape, titled "first_scrape_partial_eurlex.R", with direct input from Fergus and Marion.

**Documentation and Resources:**
- EurLex R package documentation: [CRAN](https://cran.r-project.org/web/packages/eurlex/index.html)
- EurLex Author's Git: [michalovadek.github.io/eurlex](https://michalovadek.github.io/eurlex/)
- EurLex Document Vocabularies: [EU Vocabularies](https://op.europa.eu/en/web/eu-vocabularies/concept-scheme/-/resource?uri=http://publications.europa.eu/resource/authority/resource-type)
- EurLex Chapters: [EUR-Lex Browse](https://eur-lex.europa.eu/browse/directories/legislation.html)

## 1. Install Eurlex Package and Load Dependencies

```{r install-packages, eval=FALSE}
# Install packages if not already installed
install.packages(c("eurlex", "wordcloud", "purrr", "ggiraph", "rvest", "testthat"))
```

```{r load-packages}
# Load required packages
packages <- c("dplyr", "eurlex", "ggiraph", "ggplot2", "httr", "knitr", 
              "purrr", "rmarkdown", "rvest", "testthat", "tidyr", "wordcloud")
lapply(packages, library, character.only = TRUE)
```

In our meeting, we agreed that we would predominantly rely on the function `elx_make_query` to scrape pre-legislative documents from the European Commission. The source code for this function is available [here](https://github.com/michalovadek/eurlex/blob/master/R/elx_make_query.R).

## 2. Define SPARQL Query to Retrieve Pre-Legislative Documents

We decided on using both "proposal" and "recommendation" as pre-defined resource parameters. As a manual type parameter, we are including background documents, communications, joint white papers, staff working documents, working documents, green papers, and joint green papers.

```{r define-directories}
# Define directories to search
directories <- c("02", "03", "07", "09", "11", "12", "13", "15")

# It's necessary to do this because the code expects a single unit, not a vector. 

# Directory explanations:
# 02: customs union and free movement of goods - trade measures related to climate
# 03: agriculture - agricultural policies often address climate adaptation, land use, and agricultural emissions
# 07: transport policy - transport emissions and sustainable mobility policies
# 09: financial services - green finance and climate risk regulations
# 11: external relations - international climate agreements and cooperation
# 12: energy - energy policy is intertwined with climate change, covering renewable energy, energy efficiency, and emissions
# 13: industrial policy - industrial emissions, carbon trading systems, and industrial transition policies
# 15: environment, consumers, and health protection - the most obvious location for climate change legislation
```

### Proposals Query

```{r proposals-query}
proposals_results <- map_dfr(directories, function(dir) {
  tryCatch({
    query_proposals <- elx_make_query(
      resource_type = "proposal",
      directory = dir, # Single directory per query (FIXED)
      include_date = TRUE, # Include document dates in the results
      include_author = TRUE # Include author information in the results to filter later
    )
    result <- elx_run_query(query_proposals)
    if (!is.null(result) && nrow(result) > 0) {
      result$directory_code <- dir
      return(result)
    }
    return(NULL)
  }, error = function(e) {
    return(NULL)
  })
})
```

### Recommendations Query

```{r recommendations-query}
recommendations_results <- map_dfr(directories, function(dir) {
  tryCatch({
    query_recommendations <- elx_make_query(
      resource_type = "recommendation",
      directory = dir, # Single directory per query (FIXED)
      include_date = TRUE,
      include_author = TRUE
    )
    result <- elx_run_query(query_recommendations)
    if (!is.null(result) && nrow(result) > 0) {
      result$directory_code <- dir
      return(result)
    }
    return(NULL)
  }, error = function(e) {
    return(NULL)
  })
})
```

### Manual List Query

```{r define-manual-types}
# Pre-define manual parameters
manual_types <- c("BACKGROUND_DOC", # background document related to a public consultation
                  "COMMUNIC", # non-binding document of an institution providing information
                  "COMMUNIC_DRAFT", # draft communication
                  "JOINT_PAPER_WHITE", # joint white paper 
                  "JOINT_SWD", # joint staff working document
                  "OPIN_OUTLOOK", # opinion adopted in view of pre-legislative document 
                  "PAPER_WHITE", # white paper
                  "PROP_DRAFT", # draft proposal
                  "RES_DRAFT", # draft resolution
                  "SWD", # staff working document
                  "TWD", # technical working document; unsure if I should keep this too? 
                  "WORK_DOC") # document geared towards providing information on certain policies, programmes and legislative proposals
```

```{r manual-query}
manual_results <- map_dfr(directories, function(dir) {
  map_dfr(manual_types, function(type) {
    tryCatch({
      query_manual <- elx_make_query(
        resource_type = "manual",
        manual_type = type,
        directory = dir, # Single directory per query (FIXED)
        include_date = TRUE,
        include_author = TRUE
      )
      result <- elx_run_query(query_manual)
      if (!is.null(result) && nrow(result) > 0) {
        result$directory_code <- dir
        result$manual_type_used <- type
        return(result)
      }
      return(NULL)
    }, error = function(e) {
      return(NULL)
    })
  })
})
```

## 3. Execute Queries and Combine

```{r combine-results}
if (length(proposals_results) > 0 || length(recommendations_results) > 0 || length(manual_results) > 0) {
  # Add resource type identifier to each dataset
  if (nrow(proposals_results) > 0) {
    proposals_results$resource_type_used <- "proposal"
  }
  if (nrow(recommendations_results) > 0) {
    recommendations_results$resource_type_used <- "recommendation"
  }
  if (nrow(manual_results) > 0) {
    manual_results$resource_type_used <- "manual"
  }
  # Combine all results
  combined_results <- bind_rows(
    proposals_results,
    recommendations_results,
    manual_results
  )
} else {
  combined_results <- data.frame()
}

# Check the data we scraped
str(combined_results)
print(colnames(combined_results))
```

## 4. Filter Results by Authorship and Date

I was initially mistaken, I thought if the `elx_make_query` had function calls like "include_author" and "include_date", that it would also let you filter by author and date. This just means that you have to import so much information and/or filter on the front-end, but it's no issue.

```{r filter-results}
combined_results <- combined_results %>%
  filter(date >= "1990-01-01") %>%
  filter(author == "European Commission")

# Double check the filtering
unique(combined_results$author) # shows that the EC is the only author 
combined_results$date <- as.Date(combined_results$date) # this corrals it into a date format
range(combined_results$date, na.rm = TRUE) # shows that the range is right, too 
```

## 5. Direct URL Construction and Web-Scraping Titles

As mentioned previously, there seems to be an issue with the EurLex package. Basically, it's scraping the document information, but not the name of the document or the URL, so we need to backfill those.

```{r url-construction}
# URL Construction Function 
construct_eurlex_url <- function(celex) {
  paste0("https://eur-lex.europa.eu/legal-content/EN/TXT/?uri=CELEX:", celex)
}

# Add URLs to the dataframe 
combined_results$url <- "0" # create URL column
combined_results$url <- construct_eurlex_url(combined_results$celex)
```

### Web-scraping Titles (Commented Out - Using Pre-scraped Data)

```{r web-scraping-function, eval=FALSE}
# Web-scraping Titles Function 
# scrape_eurlex_title <- function(url) {
#   tryCatch({
#     res <- GET(url, user_agent("Mozilla/5.0"))
#     page <- read_html(res)
#     # Extract from meta tag
#     title <- page %>%
#       html_node("meta[name='WT.z_docTitle']") %>%
#       html_attr("content")
#     
#     if (!is.na(title) && nzchar(title)) {
#       return(title)
#     } else {
#       return(NA)
#     }
#   }, error = function(e) {
#     message("Failed on URL: ", url)
#     return(NA)
#   })
# }
# 
# # Add titles to the dataframe
# combined_results$titles <- "0"
# combined_results$titles <- map_chr(combined_results$url, scrape_eurlex_title)
```

### Load Pre-scraped Data with URLs and Titles

```{r load-prescraped-data}
# Read in the finished dataset with titles already scraped
combined_results <- read.csv("~/Downloads/combined_results.csv", stringsAsFactors = FALSE)

# Remove the X column if it exists (row numbers from CSV)
if("X" %in% colnames(combined_results)) {
  combined_results <- combined_results %>% select(-X)
}
```

```{r save-with-titles, eval=FALSE}
# Save dataset with titles
write.csv(combined_results, "~/Downloads/combined_results.csv")
```

## 6. Fix or Remove Observations with Non-Working URLs

```{r check-non-working}
non_working_obs <- combined_results %>% filter(is.na(titles))
```

Looking at the observations where the scrape failed - just 27 in total. Using the CELEX numbers to identify and replace the title values:

```{r fix-missing-titles}
# Fix missing titles using CELEX numbers
combined_results[combined_results$celex == "52022PC0296" & is.na(combined_results$titles), "titles"] <- "Proposal for a REGULATION OF THE EUROPEAN PARLIAMENT AND OF THE COUNCIL amending Council Regulation (EC) No 1217/2009 as regards conversion of the Farm Accountancy Data Network into a Farm Sustainability Data Network"

combined_results[combined_results$celex == "52007PC0712" & is.na(combined_results$titles), "titles"] <- "Proposal for a Council Decision on the conclusion of the Agreement between the European Community and Australia on trade in wine"

combined_results[combined_results$celex == "52012PC0355" & is.na(combined_results$titles), "titles"] <- "Proposal for a DECISION OF THE EUROPEAN PARLIAMENT AND OF THE COUNCIL amending Council Decision 2008/971/EC as regards the inclusion of forest reproductive material of the 'qualified' category within the scope of that Decision and the updating of the name of the authorities responsible for the approval and control of the production"

combined_results[combined_results$celex == "52014PC0438" & is.na(combined_results$titles), "titles"] <- "Proposal for a COUNCIL DECISION on the position to be adopted on behalf of the European Union within the Council of Members of the International Olive Council concerning the prolongation of the 2005 International Agreement on olive oil and table olives"

combined_results[combined_results$celex == "52007PC0737" & is.na(combined_results$titles), "titles"] <- "Proposal for a Directive of the European Parliament and of the Council on safety rules and standards for passenger ships (Recast)"

combined_results[combined_results$celex == "51998PC0426" & is.na(combined_results$titles), "titles"] <- "Proposal for a Council Decision authorising the Portuguese Republic to apply a measure derogating from Articles 21(1)(a) and 22 of the Sixth Council Directive (77/388/EEC) of 17 May 1977 on the harmonisation of the laws of the Member States relating to turnover taxes"

combined_results[combined_results$celex == "52003PC0234" & is.na(combined_results$titles), "titles"] <- "Proposal for a Council Directive amending Directive 77/388/EEC as regards value added tax on services provided in the postal sector"

combined_results[combined_results$celex == "52023PC0342" & is.na(combined_results$titles), "titles"] <- "Proposal for a COUNCIL IMPLEMENTING DECISION amending Implementing Decision (EU) 2017/784 as regards the period of authorisation for, and the scope of, the special measure derogating from Articles 206 and 226 of Directive 2006/112/EC on the common system of value added tax taken by Italy"

combined_results[combined_results$celex == "52010PC0706" & is.na(combined_results$titles), "titles"] <- "Proposition de DÉCISION DU CONSEIL relative à la signature, au nom de l'Union Européenne, et à l'application provisoire de l'accord international sur le cacao de 2010"

combined_results[combined_results$celex == "52016PC0648" & is.na(combined_results$titles), "titles"] <- "Proposal for a COUNCIL DECISION on the signing, on behalf of the European Union, of the Agreement between the European Union and the Republic of Chile on trade in organic products"

combined_results[combined_results$celex == "52005SC1236" & is.na(combined_results$titles), "titles"] <- "Draft Decision of the EEA Joint Committee amending Protocol 31 to the EEA Agreement, on cooperation in specific fields outside the four freedoms - Draft common position of the Community"

combined_results[combined_results$celex == "52005PC0495" & is.na(combined_results$titles), "titles"] <- "Proposal for a Council Regulation terminating the partial interim review of the anti-dumping measures applicable to imports of bicycles originating in the People's Republic of China"

combined_results[combined_results$celex == "52002PC0475" & is.na(combined_results$titles), "titles"] <- "Proposal for a Council Regulation imposing definitive anti-dumping duties on imports of certain welded tubes and pipes, of iron or non-alloy steel originating in the Czech Republic, Poland, Thailand, Turkey and the Ukraine"

combined_results[combined_results$celex == "52011PC0209" & is.na(combined_results$titles), "titles"] <- "Proposition de RÈGLEMENT DU CONSEIL instituant un droit antidumping définitif sur les importations de furfural originaire de la République populaire de Chine à l'issue d'un réexamen au titre de l'expiration des mesures effectué en vertu de l'article 11, paragraphe 2, du règlement (CE) n° 1225/2009"

combined_results[combined_results$celex == "51996PC0324" & is.na(combined_results$titles), "titles"] <- "Proposal for a COUNCIL REGULATION (EC) providing for the reduction of the tariff rate applicable to imports under the WTO tariff quota for certain live bovine animals"

combined_results[combined_results$celex == "52002PC0003(03)" & is.na(combined_results$titles), "titles"] <- "Proposal for a Council Regulation adopting autonomous measures concerning the importation of fish and fishery products originating in the Republic of Hungary"

combined_results[combined_results$celex == "51991PC0074" & is.na(combined_results$titles), "titles"] <- "PROPOSAL FOR A COUNCIL REGULATION (EEC) AMENDING COUNCIL REGULATION (EEC) 2340/90 OF 8 AUGUST 1990 AND COUNCIL REGULATION (EEC) 3155/90 OF 29 OCTOBER 1990 PREVENTING TRADE BY THE COMMUNITY AS REGARDS IRAQ AND KUWAIT"

combined_results[combined_results$celex == "52011PC0197" & is.na(combined_results$titles), "titles"] <- "Proposal for a COUNCIL REGULATION imposing a definitive anti-dumping duty and collecting definitively the provisional duty imposed on imports of melamine originating in the People's Republic of China."

combined_results[combined_results$celex == "52007PC0098" & is.na(combined_results$titles), "titles"] <- "Proposal for a Council and Commission Decision on the conclusion of the Protocol to the Partnership and Cooperation Agreement between the European Communities and their Member States, of the one part, and Georgia, of the other part, to take account of the accession of the Republic of Bulgaria and Romania to the European Union"

combined_results[combined_results$celex == "52013PC0543" & is.na(combined_results$titles), "titles"] <- "Proposal for a COUNCIL DECISION extending the validity of Decision 2012/96/EU"

combined_results[combined_results$celex == "52013PC0040" & is.na(combined_results$titles), "titles"] <- "Proposal for a REGULATION OF THE EUROPEAN PARLIAMENT AND OF THE COUNCIL amending Regulation (EU) No 912/2010 setting up the European GNSS Agency"

combined_results[combined_results$celex == "52007PC0856" & is.na(combined_results$titles), "titles"] <- "Proposal for a Regulation of the European Parliament and of the Council setting emission performance standards for new passenger cars as part of the Community's integrated approach to reduce CO2 emissions from light-duty vehicles"

combined_results[combined_results$celex == "52000PC0394" & is.na(combined_results$titles), "titles"] <- "Proposal for a Regulation of the European Parliament and of the Council on unbundled access to the local loop"

combined_results[combined_results$celex == "52008PC0302" & is.na(combined_results$titles), "titles"] <- "Proposal for a Council Regulation repealing Council Regulation (EC) No 752/2007 of 30 May 2007 on administering certain restrictions on imports of certain steel products from Ukraine"

combined_results[combined_results$celex == "52015XC0327(04)" & is.na(combined_results$titles), "titles"] <- "Commission communication concerning Article 4(3) of Directive 2009/22/EC of the European Parliament and of the Council on injunctions for the protection of consumers' interests, which codifies Directive 98/27/EC, concerning the entities qualified to bring an action under Article 2 of this Directive Text with EEA relevance"

combined_results[combined_results$celex == "52013DC0659" & is.na(combined_results$titles), "titles"] <- "COMMUNICATION FROM THE COMMISSION A new EU Forest Strategy: for forests and the forest-based sector"

combined_results[combined_results$celex == "52011XC0205(05)" & is.na(combined_results$titles), "titles"] <- "Publication of an application pursuant to Article 6(2) of Council Regulation (EC) No 510/2006 on the protection of geographical indications and designations of origin for agricultural products and foodstuffs"
```

## 7. Check Other Missing Values

```{r check-missing-values}
# Check the dataset structure
summary(combined_results)

# Identify other missing values
sapply(combined_results, function(x) sum(is.na(x)))

# The only missing values should be in the manual_type_used column
na_manual_type <- combined_results %>% filter(is.na(manual_type_used))
unique(na_manual_type$resource_type_used) # This assures us that there weren't any issues with the scrape
```

## 8. Deduplication based on CELEX Number

The easiest way to deduplicate is based on CELEX number, since each EurLex document has a unique identification code.

```{r check-duplicates}
all_duplicates <- combined_results %>% 
  group_by(celex) %>% 
  filter(n() > 1) %>% 
  arrange(celex)

# Remove duplicates based on CELEX number
deduplicated_results <- combined_results %>% distinct(celex, .keep_all = TRUE)

# Verify deduplication worked
all_duplicates_check <- deduplicated_results %>% 
  group_by(celex) %>% 
  filter(n() > 1) %>% 
  arrange(celex) # Should be empty now
```

## 9. Analysis of Title Duplicates

```{r title-duplicates-analysis}
# Check for exact text duplicates in titles
title_duplicates <- deduplicated_results %>%
  group_by(titles) %>%
  filter(n() > 1) %>%
  arrange(titles)

# Sample some duplicates for manual inspection
title_duplicates <- title_duplicates %>% ungroup()
set.seed(20)
title_sample <- title_duplicates %>% slice_sample(n = 20)
```

After manual inspection of the title duplicates, we determined that documents with the same titles but different CELEX numbers are actually different documents (e.g., different versions, amendments, or separate notifications), so we should not deduplicate based on titles.

## 10. Save Final Dataset

```{r save-final}
write.csv(deduplicated_results, "~/Downloads/deduplicated_scrape.csv", row.names = FALSE)

# Display final dataset summary
cat("Final dataset contains", nrow(deduplicated_results), "unique documents\n")
cat("Date range:", min(deduplicated_results$date, na.rm = TRUE), "to", max(deduplicated_results$date, na.rm = TRUE), "\n")
cat("Resource types:", paste(unique(deduplicated_results$resource_type_used), collapse = ", "), "\n")
```

## Summary

This R Markdown document successfully:

1. Loaded the EurLex R package and dependencies
2. Queried EU pre-legislative documents across multiple directories and resource types
3. Combined and filtered results by authorship (European Commission) and date (from 1990)
4. Constructed URLs and incorporated pre-scraped titles
5. Fixed missing title values manually
6. Deduplicated based on CELEX numbers
7. Analyzed title duplicates and determined not to remove them
8. Saved the final cleaned dataset

The final dataset contains legislative documents that can be used for further analysis of EU climate and environmental policy development.